Effects of the body force on the evacuation dynamics

### 2020-02-04 paper.tex
mejore la redaccion de la parte final de resultados

The empirical measurements correspond to the fundamental diagram at the entrance of the Jamaraat bridge (see the inset in Fig.~\ref{flow_density_no_body_force}). We aim to reproduce the qualitative behavior of these measurements roughly.\\

@@

According to most of the empirical measurements of the fundamental diagram, the flow decreases for high enough values of density because the crowd becomes jammed. Notice that the original friction (corresponding to $\mathcal{K}=$137) does not produce a reduction of the flow when there is zero body force ($\mathcal{K}_c=$0). Nevertheless, when the body force is included, and we remain the original friction (circles from Fig.~\ref{flow_density_body_force}), the flow reduces from  5 p m$^{-2}$ to 7 p m$^{-2}$ and then increases for higher values of density.\\

@@

These results suggest that although increasing $\mathcal{K}_c$ produces a reduction in the flow, it is necessary to increase $\mathcal{K}$ (for instance, increasing friction $k_t$) to reproduce the reduction in the flow that characterizes the high-density regime. It is still a pending challenge to find the values of the dimensionless numbers that reproduce the qualitative behavior of the fundamental diagram, but this first approach narrows down the search.\\

>>>>

The empirical measurements correspond to the fundamental diagram measured at the entrance of the Jamaraat bridge (see the inset in Fig.~\ref{flow_density_no_body_force}). We aim to reproduce the qualitative behavior of these measurements roughly.\\

@@

According to most of the empirical measurements of the fundamental diagram, the flow decreases for high enough values of density because the crowd becomes jammed. Notice that the original friction (corresponding to $\mathcal{K}=$137) does not produce a reduction of the flow when there is zero body force ($\mathcal{K}_c=$0). Nevertheless, when the body force is included, and we remain the original friction (circles from Fig.~\ref{flow_density_body_force}), the flow reduces in the range of densities from  5 p m$^{-2}$ to 7 p m$^{-2}$; then increases for higher values of density.\\

@@

These results suggest that although increasing $\mathcal{K}_c$ produces a reduction in the flow, it is necessary to increase $\mathcal{K}$ (for instance, increasing the friction coefficient $k_t$) to reproduce the reduction in the flow that characterizes the high-density regime. It is still a pending challenge to find the values of the dimensionless numbers that reproduce the qualitative behavior of the fundamental diagram, but this first approach narrows down the search.\\
